---
title: "Testing rendering environments in rmarkdown"
output: html_document
---

Since I am rendering the vignette as follow:
```{r, eval=FALSE}
vignette_env <- new.env(parent = as.environment("package:stats"))
vignette_path <- rmarkdown::render(path_complete, quiet = TRUE, envir = vignette_env)
```

I would expect not to find my package in the namespace here, nor the global env:

Yet, my package appears among the attached ones (before loading the package) in the vignette:
```{r}
search()
```

Question 1: why is my package attached?

Since my package is attached, I would expect `hello()` to work, but it does not:
Attempt at using `hello()` before loading the package:
```{r, error=TRUE}
hello()
```

Question 2: why is `hello()` not found?

I now load the package:
```{r, error=TRUE}
library(testenvrmarkdown)
```

Nothing seems to happen:
```{r}
search()
```

Another attempt at using `hello()` after loading the package:
```{r, error=TRUE}
hello()
```

Question 3: why is `hello()` still not found?

